---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file and render with rmarkdown::render("README.Rmd")-->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Climate Change Decent Work and Workers Health (CLIDEWO)

Source code for [personal website of Edgar Rodriguez Huerta].

Created with [Quarto](https://quarto.org/) in [R](https://www.r-project.org/). 


## Local deployment

- Generate the translated website with `babelquarto::render_website()`

- Preview the website with `servr::httw("_site")`

## Drafting a new blogpost

Use the [custom `draft_post()` function](R/functions.R):

```{r}
post_qmd <- draft_post(
  slug = "example_post",
  title = "How to use the draft_post() function",
  desc = "Using templates to increase productivity",
  categories = c("R", "data")
)
readr::read_lines(post_qmd)
fs::dir_delete(fs::path_dir(post_qmd))
```

## Licenses

Code: [MIT](LICENSE)

Text and images, unless otherwise indicated: Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/legalcode)

Publications (PDF files): Indicated in each publication.